---
title: "Student Sit In"
author: "Cortajha Hunter"
date: "10/26/2019"
output: 
  html_document:
    toc: true
    number_sectons: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ONE SHOT assignment!
this is an extra credit assignment, must be completed Monday Oct 28, turn-in closes at midnight!

## Problem statement: 
Students at UCD- is there a relation between where one sits and one's major? 

## Introduction  

<!-- where is the data found?  Is this an experiment or an observational study?  !-->

Data from this study came from UC Davis, in which there was 173 students.



```{r include=FALSE, echo=FALSE}
library(tigerstats)
data(ucdavis1)

```

$H_0$: there is no relationship between one's major and where one sits in a class   
$H_A$: where one sits in class and one's major are related  

<!-- Get the data: !-->

## Methods

<!--  describe analysis methods here 
what are the variable types, and indicate gaphical, numerical, and inferential methods appropriate
for this question  !--> 

In this data chart; the percentage of student were either enrolled into Liberal Arts or Non-Liberal Art and it shows the percentages of the students who sat in the back, front, and middle of the classroom. 

## Data summary

**Graphical summary**
put the graphic description of the data here

In the graph, apporximately 80% of students that sat in back, front and middle of the classroom were Non-Liberal.


```{r echo=FALSE}
barchartGC(~Seat+class, data=ucdavis1, main='ucdavis$seats', type='percent', xlab='SEAT')
```

Explain what the graph shows

There were about 35% of student who sat in the back, front, and middle who were in Liberal Arts. 



**Numerical summary**
put numerical summary here

```{r}
tab=xtabs(~Seat+class, data=ucdavis1)
print(tab)

```

Explain what the numeric summary says that the student whom are in Liberal Arts shows similar, yet low numbers, while there is an increase in the Non-Liberal students. 

## Inferential Results
put the inferential test for the the null hypothesis here

```{r}
chisqtestGC(tab)
```

what is the p-value? .22 > .05

## Results and conclusions

<!-- explain-- is there evidence that certain majors tend to sit in particular areas of the class?  Can the results of this test be generalized to all majors in all universities? !-->

explain the result, can the result be generalized?

The students from UC Davis 

<!--
push results to your github account, turn in the URL

--OR--

If you did not fork my repo to your github account,
create a repository in your github account for this project, get the URL for that repo and 
(in the terminal window..)

$git remote add origin URL_of_your_github_repo
$git push -u origin master

!-->